The Resurgence of the Linear Optics Interferometer --- Recent Advances \& Applications

### 2017-04-25 paper.tex
Started section on single photon sources.

\sihui{ SPDC, quantum-dot micropillar sources}

>>>>

Sources of single photons for applications of quantum information processing are 
separated into two main categories \cite{bib:Kok05}; those produced by spontaneous 
parametric down-conversion (SPDC), and those by solid-state emitters in a cavity. 
Both categories have seen some leaps recently in their record production of numbers 
of single photons while preserving good qualities in their single photons. To 
date, SPDC has been able to produce up to ten entangled photons 
\cite{bib:WangChen16,bib:Chen17}, and five-photon quantum interference has been 
reported using a quantum dot emitter in a microcavity \cite{bib:WangHe16}.

In SPDC, a nonlinear crystal with a large $\chi^{(2)}$ is pumped with a strong 
laser and with a small probability, the pump beam is absorbed by the crystal to 
produce two beams of lower energy known as the signal and idler beams. Owing to 
conservation of energy and momentum, the two beams have spatio-temporal 
correlations that can be engineered to produce twin-beam states which have 
perfectly correlated photon numbers. If a single photon were to be detected in one 
of the beams, and then it is certain that the other beam would be in the state of a 
single photon. Some commonly used nonlinear crystals for SPDC are beta barium 
borate (BBO), periodically poled lithium niobate (PPLN), and periodically poled 
potassium titanyl phosphate (PPKTP). Recently, techniques using bismuth triborate 
(BiBO) have improved to the extent of becoming one of the record-holders of single-
photon production.
\cite{bib:WangChen16}.
